State of the Practice for Medical Imaging Software

### 2022-03-25 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Updates to SOP for MI paper

\section{Comparison Between LBM and Research Software for Artifacts}
\label{Sec_CompareArtifacts}

@@

\section{Comparison of Tool Usage Between LBM and Other Research Software}
\label{Sec_CompareTools}

@@

@@

\subsection{Current and Past Pain Points} \label{sec_interview_pain_points}

@@

\begin{description}
\item[RQ1.] What artifacts are present in current software projects?
\end{description}

>>>>

\section{Comparison Between MI and Research Software for Artifacts}
\label{Sec_CompareArtifacts}

@@

\section{Comparison of Tool Usage Between MI and Other Research Software}
\label{Sec_CompareTools}

@@

\section{Developer Pain Points} \label{painpoints}

Based on interviews with four developers, this section aims to answer the
research questions: i) What are the pain points for developers working on
research software projects (\rqref{RQ_PainPoints})?; and, ii) How do the pain
points of developers from LBM compare to the pain points for research software
in general (\rqref{RQ_ComparePainPoints})?  Below we go through each of the
identified pain points and include citations that contrast the LBM experience
with observations from researchers in other domains.  Potential ways to address
the pain points are covered in Section~\ref{Sec_AddressConcerns}. The full
interview questions are found in \citet{SmithEtAl2021}.

@@

%\label{sec_interview_pain_points}

@@
